\chapter{Acknowledgements}\label{ch:Acknowledgements}

I am both excited and intimidated at the daunting task of writing the acknowledgements, having finished the relatively easy task of finishing the thesis itself. I have spent the last six years here in Leuven, and these have been some of the best years of my life. As eager as I am to put the metaphorical pen down, I would like to take the spacetime (time and space, hehe) to thank the people who made this journey possible.

First of all, a huge thank you to Hugues for giving me the opportunity to pursue this PhD. You have been the best supervisor a PhD student could ask for, and I thank you for letting me find my academic path with gentle nudges and your endless wisdom. You have always been understanding about my non-traditional holiday periods, and I am very grateful for that. Tomer, thank you for being extremely patient, bearing with my never-ending questions and taking the time to walk me through a lot of theory. Thanks for all of the good times and great food, and hopefully more to come! A huge thank you to my jury members - Paul, Nicole, Pierre and Jon, for making the defense a positive experience for me, as well as for the extremely helpful comments and guidance throughout the years.

I would like to thank Anita and Monique for their superhuman efforts with respect to the mountain of admin that they have helped me with. Renewing my contract every single year must have been cumbersome, as well as dealing with all of the reimbursements. Thank you for being patient and ever-willing to help me.

When I first arrived in Belgium, I was nervous about this cold, dark country. Nico my duderino, thank you for being the ever-friendly Belgian who never failed to tease me about my intolerance to the cold. I will fondly remember the nights at IvS working on projects along with Gilles, with ping pong (and cara) sessions in between. Billy and Gwenael, thanks for our long evenings of exchanging cultural food (the only time I ever ate or will eat witloof) and for taking me bar hopping to find a Belgian beer I would like. I can happily say that you guys succeeded! Nena, Bertold and Ada - thank you for the constant comfort and company without which I wouldn't have survived Belgium. I always felt at home with you, and thanks for all of the crazy stories swapped, the potlucks, driving across the country to sample good food and the patience with which you explained the hot mess that is Belgium! Nozomi-kun, thank you for your friendship over the years. Your hard work and determination is a constant source of inspiration, and I am extremely thankful for all of the sleepovers and study sessions in Agora.

Ana and Shreeya, thanks for taking me under your wings and teaching me the ins and outs of academia. Thank you for our endless gossip sessions, the delicious food and for the constant companionship in the best office ever. Speaking of the best office ever, thanks to Dylan, Jordan, Joonas and Mathias for making it memorable over the years. Olivier, Jolien and Frank, thanks for the semblance of normalcy after we returned to the office! Michael, thanks for being the best roommate ever during conferences, as well as for all of the jokes and game sessions. Mike and Jels, I often reminisce our discussions (rants) about academia, along with discussions on python (particularly colour schemes, VIRDIS $>$ inferno?). Cole and Andrew, thank you for making my La Palma trip one of the more memorable courses in the Masters (and the ping pong!), as well as for welcoming me into the weekly IvS basketball games. I hope we can play together again soon! Glenno, thank you for putting up with my abysmal football skills for the times we played (and for the league)! Matthias, Joey, Clio, Emily, Vasilya, Rema and May, thanks for fun badminton games.

Having a pandemic and a lockdown during a 4-year PhD is unfortunate, and there are a bunch of people without whom I definitely would not have survived this. A huge thank you to all those who sportingly took part in and organised the nascent IvS quizzes. I still have the screenshots, and chuckle about the flag-drawing contest among others. To my brothers-in-arms who started this journey along with me - Siemen, Calum, Gareth and JP among others. Thank you for the memorable receptions, the karaoke, the late nights at Oude, Rocket League$^{\textrm{TM}}$, smash bros and Xbox nights. Abi and Ffion, thanks for obsessing over cats, street food and screaming on roller coasters with me.

I would also like to thank all of the members of SPAM - Hugues, Tomer, Laurent, Jaime, Maddalena, Calum, Cyprien, Dominic, Annachiara, Gareth, Emma, Frank, Soetkin, Tinne, Pablo, Michael, Julia, Matthias and Abi. Thanks for the group meetings with cake, the scientific discussions, group dinners, our own Uitje and the numerous conferences we've been to. Cheers to the black-hole killers!

Robin and Katlien, thank you for the dosa nights, Blokhut nights and the volleyball lessons! Barney, thanks for teaching me MTG, the endless coffee, discussions on work-life balance (haha) and trading your absolutely mind-blowing dark-chocolate sea-salt cookies for Indian food during the lockdown. To Robin, Katlien, Nico, Nicho, Tess, Annachiara, Danny, Jolien, Silke, Romain, Pablo, Sara and Matthias, thank you for the weekly volleyball games and wind-down at the Spuye. I will forever train my placement skills until I grow tall enough to smash.

Vasilya, Sonya, I am so glad I met you guys! Thank you for the badminton and the fun potlucks. It's bittersweet that you're moving away from Leuven but I am sure we will catch up regularly. I would also like to thank the Humans of Nalasopara - Sumi, Sur and Gayu, our daily video calls and shenanigans, along with our yearly (monthly?) trips were some of our favourite times. Similarly, Manasa, Pinku, Avni and Neha, thank you for the regular video calls, providing me with the vital hot goss that allowed me to finish my PhD.

Julia and Emily, thank you for the endless coffee trips, even when it was $-8\degree$\,C outside. Thank you for hanging out, keeping me sane and keeping my goals realistic during the lockdown. Nicholas, thanks for patiently taking me through basic house repairs, for turning every social gathering into Barraquito-night, and for constantly filling out my freezer with ice cream. Dominic, thank you for being a mentor and a friend with a similar sense of humour (as I was surprised to discover).

Pablo and Sara, thank you for nerding out on anime and manga with me, as well as your endless wisdom related to cats, plants and life. Thank you for introducing me to pickled onions and paprika, and for convincing me to get two kittens instead of one. I am forever in your debt. Yannis and Mathias, Solo Leveling shall forever be the greatest (after One Piece). Thank you for the daily discord, memes, songs, and video games during and after the lockdowns. Luka, thanks for the endless conversations and (short) walks. I promise to go on a long walk with you at some point, although definitely not the 100 km one.

Rema, Oli, you guys rock. I need to say this on paper so that you don't stab me with a pair of scissors (I'll see myself out now). Thank you for the chess, mahjong, trashy chef videos, all of the food and, most importantly, Salem.

Adi, we started this journey together when we sat together and googled universities to apply to. From there to the dozens of day-trips, dancing on the streets of Oslo, to ready-to-eat food and pretending to be Ranveer Brar, we've done it all. I expect a whole chapter in your autobiography, nothing less.

Last but not least, a big thank you to my family for your unconditional love and belief in me. Mom, thanks for supporting and enabling me to pursue my dream. Daat, thank you for your constant encouragement and interest in my work. Kofta and Kulfi must be mentioned, since they are the best emotional support I could ask for.

Perhaps the most important of all, thank you Kani. For your everlasting patience with my puns, for the support during the stressful times and your infectious morning energy.

Thank you again, everyone. I am happy to have shared this journey with you.

Karan


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keep the following \cleardoublepage at the end of this file,
% otherwise \includeonly includes empty pages.
\cleardoublepage

% vim: tw=70 nocindent expandtab foldmethod=marker foldmarker={{{}{,}{}}}
